Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-03 lqg-strings.tex
finished quantization of area corrected string and bimetric appendix in main file

Looking closer at our Virasoro-like \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
\begin{multline} \label{eqn:string-rest-mass-classical-1}
	M^2 = - p^{\mu} p_{\mu} = - \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n , n} \right) - \\
	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) =
\end{multline}
\begin{multline} \label{eqn:string-rest-mass-classical-2}
	= - \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \\
	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) .
\end{multline}

@@

We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
\begin{multline} \label{eqn:canonical-momentum-density}
	\Pi ^{\nu} (x) = F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \bigg( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \\
	- (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \bigg)
\end{multline}
where
\begin{multline} \label{eqn:F-minus-full-sum}
	F^{-} = 1 - \frac{k \Delta}{2 \e ^{\phi (x)}} = \\
	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
\end{multline}
and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
\begin{equation} \label{eqn:canonical-bracket-relation}
	\left\{ X^{\mu} (0 , \sigma) , \Pi ^{\nu} (0 , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$. After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
\begin{equation} \label{eqn:expansion-modes-bracket-0}
	\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\} = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\}
\end{equation}
\begin{equation} \label{eqn:expansion-modes-bracket-1}
	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{m} \delta _{|m| , |p|} \eta ^{\mu \nu} = - \left\{ (\alpha ^{\mu} _{n})^{*} , \alpha ^{\nu} _{p} \right\} ,
\end{equation}
from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
\begin{align}
	a^{\mu} _{n}       & := \frac{1}{\sqrt{E_{n}}} \alpha ^{\mu} _{n} \label{eqn:normalized-oscillator-modes}         \\
	(a^{\mu} _{n})^{*} & := \frac{1}{\sqrt{E_{n}}} (\alpha ^{\mu} _{n})^{*} \label{eqn:normalized-oscillator-modes-*}
\end{align}
\begin{equation} \label{eqn:harmonic-bracket-relations}
	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|m| , |l|} \eta ^{\mu \nu} .
\end{equation}
The bracket relations for $\alpha ^{\mu} _{0}$ can be used to get the expected bracket relations between $x^{\mu}$ and $p^{\nu}$
\begin{align}
	\left\{ x^{\mu} , x^{\nu} \right\} & = 0 = \left\{ p^{\mu} , p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
	\left\{ x^{\mu} , p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
\end{align}

@@

As usual, we define the vacuum state of the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
\end{equation}
For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
\begin{align}
	\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-vacuum-x}                       \\
	\Hat{p}_{\mu} \ket{0 ; 0} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
\end{align}
in position representation and
\begin{align}
	\Hat{x}^{\mu} \ket{0 ; p} & = i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-vacuum-p}
\end{align}
in momentum representation.

@@

When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators. As for $\widetilde{L}_{p , k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
\end{equation}
This ambiguity manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n , n} \right) - a \right) \ket{\psi} = 0 ,
\end{equation}
for some constant $a$. Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by
\begin{multline} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = \frac{8}{\alpha '} \Bigg( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
	- \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Bigg) .
\end{multline}
This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
\begin{equation}
	a = D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} .
\end{equation}

@@

Let us denote the ground state with momentum $p^{\mu}$ by $\ket{0 ; p}$. Then, the mass-shell condition \eqref{eqn:shifted-mass-spectrum} implies that
\begin{equation} \label{eqn:ground-state-mass-shell}
	\frac{\alpha '}{8} p^2 = - \left( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 + a \right) .
\end{equation}
Next we look at the $n$-th excited state $\zeta _{\mu} (\Hat{a}^{\mu} _{d})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The mass-shell now reads
\begin{multline} \label{eqn:nth-state-mass-shell}
	\frac{\alpha '}{8} M^2 = - \Bigg( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 - \\
	- 4 \sinh ^2 \left( \frac{1}{4} \ln (n^2 + \mu ^2) \right) + a \Bigg) ,
\end{multline}
while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ implies that
\begin{equation} \label{eqn:zeta-p-psi}
	\zeta _{\mu} p^{\mu} = - \frac{4 \mu}{\alpha '} \zeta _{\mu} \frac{\partial \psi (p)}{\partial p_{\mu}} .
\end{equation}
If the momentum wave-function is taken to be
\begin{equation} \label{eqn:p-wave-function}
	\psi (p) = - \frac{\alpha '}{8 \mu} p^{\mu} p_{\mu} ,
\end{equation}
eq \eqref{eqn:zeta-p-psi} reduces to $\zeta _{\mu} p^{\mu} = 0$. Putting this back in the mass-shell yields
\begin{equation} \label{eqn:ground-state-mass-shell-simplified}
	\frac{\alpha '}{4} p^2 = - a
\end{equation}
for the ground state and
\begin{equation} \label{eqn:nth-mass-shell-simplified}
	\frac{\alpha '}{4} p^2 = 4 \sinh ^2 \left( \frac{1}{4} \ln (n^2 + \mu ^2) \right) - a
\end{equation}
for the $n$-th state. The norm of these states is given by $\zeta _{\mu} \zeta ^{\mu}$, so if we choose $p^{\mu}$ to lie on the $(0 , 1)$-plane, then the $D - 2$ spacelike polarizations normal to said plane have positive norm. If $a$ is chosen such that the $n = d , d = D - 1$ excited state is a tachyon with $p^2 > 0$, then $p^{\mu}$ can be taken to have no time component, leaving $\zeta _{\mu}$ timelike with negative norm. If the choice is made such that $p^2 < 0$, $p^{\mu}$ can be chosen to have only a time component, making $\zeta _{\mu}$ spacelike with positive norm again. At last, if we choose for $p^2 = 0$, then $\zeta _{\mu}$ is proportional to $p^{\mu}$ with 0 norm, so for the absence of ghosts we require that
\begin{equation} \label{eqn:c-no-ghost-spin-1}
	a \geq 4 \sinh ^2 \left( \frac{1}{4} \ln (d^2 + \mu ^2) \right) .
\end{equation}
In the boundary case, the $d$-th excited vector state is massless and all other vector states (plus the ground state) are regular massive particles with $M^2 > 0$. This, however, is to get a massless vector state for the closed string. The actual massless particle we want from the closed string is a symmetric, traceless spin-2 particle, so let's now consider the state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ where $\zeta _{\mu \nu}$ is the polarization tensor. The mass-shell reads
\begin{equation} \label{eqn:dth-spin-2-mass-shell}
	\frac{\alpha '}{4} p^2 = 8 \sinh ^2 \left( \frac{1}{4} \ln (d^2 + \mu ^2) \right) - a
\end{equation}
and the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{d , 0} \zeta _{\mu \nu} (\Hat{a}^{\mu} _{d})^{\dagger} (\Hat{a}^{\nu} _{d})^{\dagger} \ket{0 ; p}$ together with the momentum wave-function \eqref{eqn:p-wave-function} implies
\begin{equation}
	\zeta _{\mu \nu} p^{\mu} = 0 .
\end{equation}
We can decompose the polarization into a symmetric traceless part $G_{\mu \nu} = G_{\nu \mu} , \eta ^{\mu \nu} G_{\mu \nu} = 0$, a anti-symmetric part $B_{\mu \nu} = - B_{\nu \mu}$ and a trace part $\Phi \eta _{\mu \nu} , \Phi = \eta ^{\alpha \beta} \zeta _{\alpha \beta} / D$, $\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-knwon types of background fields: the graviton $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$.

@@

Following the general procedure, given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
\begin{equation}\label{eqn:polyakov-curved}
	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
\begin{align}\label{eqn:polyakov-flat}
	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber \\
	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}.
\end{align}

>>>>

Looking closer at our Virasoro-like \textquotedblleft modes", in particular the $n = p$ condition, we get the mass of the string in terms of its vibrational modes and center of mass position
\begin{multline} \label{eqn:string-rest-mass-classical-1}
	M^2 = - p^{\mu} p_{\mu} = \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \widetilde{L}_{n , n} \right) - \\
	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) =
\end{multline}
\begin{multline} \label{eqn:string-rest-mass-classical-2}
	= \frac{4}{\alpha '} \Bigg( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) - \\
	- \frac{2 \mu ^2}{\alpha '} x^{\mu} x_{\mu} \Bigg) .
\end{multline}

@@

We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
\begin{multline} \label{eqn:canonical-momentum-density}
	\Pi ^{\nu} (x) = F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \bigg( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \\
	- (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \bigg)
\end{multline}
where
\begin{multline} \label{eqn:F-minus-full-sum}
	F^{-} = 1 - \frac{k \Delta}{2 \e ^{\phi (x)}} = \\
	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
\end{multline}
and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
\begin{equation} \label{eqn:canonical-bracket-relation}
	\left\{ X^{\mu} (0 , \sigma) , \Pi ^{\nu} (0 , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$. After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
\begin{equation} \label{eqn:expansion-modes-bracket-0}
	\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\} = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\}
\end{equation}
\begin{equation} \label{eqn:expansion-modes-bracket-1}
	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} ,
\end{equation}
from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
\begin{align}
	a^{\mu} _{n}       & := \frac{1}{\sqrt{E_{n}}} \alpha ^{\mu} _{n} \label{eqn:normalized-oscillator-modes}         \\
	(a^{\mu} _{n})^{*} & := \frac{1}{\sqrt{E_{n}}} (\alpha ^{\mu} _{n})^{*} \label{eqn:normalized-oscillator-modes-*}
\end{align}
\begin{equation} \label{eqn:harmonic-bracket-relations}
	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|m| , |l|} \eta ^{\mu \nu} .
\end{equation}
The bracket relations for $\alpha ^{\mu} _{0}$ can be used to get the expected bracket relations between $x^{\mu}$ and $p^{\nu}$
\begin{align}
	\left\{ x^{\mu} , x^{\nu} \right\} & = 0 = \left\{ p^{\mu} , p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
	\left\{ x^{\mu} , p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
\end{align}

@@

As usual, we define the vacuum state of the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
\end{equation}
For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
\begin{align}
	\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-vacuum-x}                       \\
	\Hat{p}_{\mu} \ket{0 ; 0} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
\end{align}
in position representation and
\begin{align}
	\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-vacuum-p}
\end{align}
in momentum representation.

@@

When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators. As for $\widetilde{L}_{p , k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
\end{equation}
This ambiguity manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n , n} \right) - a \right) \ket{\psi} = 0 ,
\end{equation}
for some constant $a$. Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by
\begin{multline} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = \frac{8}{\alpha '} \Bigg( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
	- \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Bigg) .
\end{multline}
This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
\begin{multline}
	a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \\
	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} .
\end{multline}

@@

Let us denote the ground state with momentum $p^{\mu}$ by $\ket{0 ; p}$. Then, the mass-shell condition \eqref{eqn:shifted-mass-spectrum} implies that
\begin{equation} \label{eqn:ground-state-mass-shell}
	\frac{\alpha '}{8} p^2 = \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 + a .
\end{equation}
Next we look at the $n$-th excited vector state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution doesn't have independent left and right sectors, thus permitting spin-1 states. We'll discuss these closed string single excitation states in section \ref{sec:discussion}. The mass-shell now reads
\begin{multline} \label{eqn:nth-state-mass-shell}
	\frac{\alpha '}{8} M^2 = \Bigg( \frac{2 \mu ^2}{\alpha '} \left| \frac{\partial \psi (p)}{\partial p} \right| ^2 - \\
	- \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} + a \Bigg) ,
\end{multline}
while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ implies that
\begin{equation} \label{eqn:zeta-p-psi}
	\zeta _{\mu} p^{\mu} = - \frac{4 \mu}{\alpha '} \zeta _{\mu} \frac{\partial \psi (p)}{\partial p_{\mu}} .
\end{equation}
If the momentum wave-function is taken to be
\begin{equation} \label{eqn:p-wave-function}
	\psi (p) = - \frac{\alpha '}{8 \sqrt{2} \mu} p^{\mu} p_{\mu} ,
\end{equation}
eq \eqref{eqn:zeta-p-psi} reduces to $\zeta _{\mu} p^{\mu} = 0$. Putting this back in the mass-shell yields
\begin{equation} \label{eqn:ground-state-mass-shell-simplified}
	\frac{\alpha '}{16} p^2 = a = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k}
\end{equation}
for the ground state and
\begin{multline} \label{eqn:nth-mass-shell-simplified}
	\frac{\alpha '}{16} p^2 = a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} = \\
	= - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n}
\end{multline}
for the $n$-th state. The norm of these states is given by $\zeta _{\mu} \zeta ^{\mu}$, and since by eq \eqref{eqn:nth-mass-shell-simplified} we see that $p^2 < 0$, thus $\zeta ^2 > 0$ always holds and we have no ghosts in the closed string spin-1 spectrum. This analysis, however, is for vector states from the closed string. The actual particle we want from the closed string is a symmetric, traceless spin-2 particle, so let's now consider the state $\zeta _{\mu \nu} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \ket{0 ; p}$ where $\zeta _{\mu \nu}$ is the polarization tensor. The mass-shell reads
\begin{equation} \label{eqn:nth-spin-2-mass-shell}
	\frac{\alpha '}{16} p^2 = - D \sum _{k > 0} \left( 1 + \frac{k^2}{E_{k} ^2} \right) E_{k} - 4 \left( 1 + \frac{n^2}{E_{n} ^{2}} \right) E_{n} .
\end{equation}
The auxiliary $\bra{0 ; p} \xi _{\alpha} \Hat{a}^{\alpha} _{n} \Hat{\widetilde{L}}_{n , 0} (\Hat{a}^{\mu} _{n})^{\dagger} (\Hat{a}^{\nu} _{n})^{\dagger} \zeta _{\mu \nu} \ket{0 ; p} = 0$ condition where $\xi _{\alpha}$ is a arbitrary polarization for the auxiliary vector excitation implies that
\begin{equation} \label{eqn:spin-2-zeta-p=0}
	(\zeta _{\mu \nu} + \zeta _{\nu \mu}) p^{\mu} = 0 .
\end{equation}
We can decompose the polarization into a symmetric traceless part $G_{\mu \nu}$, an anti-symmetric part $B_{\mu \nu}$ and a trace part $\Phi \eta _{\mu \nu}$ given by
\begin{align}
	G_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} + \zeta _{\nu \mu}) - \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \eta _{\mu \nu} \label{eqn:G-zeta} \\
	B_{\mu \nu} & = \frac{1}{2} (\zeta _{\mu \nu} - \zeta _{\nu \mu}) \label{eqn:B-zeta}                                                                          \\
	\Phi        & = \frac{1}{D} \eta ^{\alpha \beta} \zeta _{\alpha \beta} \label{eqn:Phi-zeta} ,
\end{align}
$\zeta _{\mu \nu} = G_{\mu \nu} + B_{\mu \nu} + \Phi \eta _{\mu \nu}$, giving rise to 3 well-known types of background fields: the spacetime metric $G_{\mu \nu}$, Kalb-Ramond 2-form $B_{\mu \nu}$ and dilaton $\Phi$, all of those having squared mass given by eq \eqref{eqn:nth-spin-2-mass-shell}. We thus see that the symmetric part $S_{\mu \nu} = G_{\mu \nu} + \Phi \eta _{\mu \nu}$ of $\zeta _{\mu \nu}$ is orthogonal to the momentum of the string, $S_{\mu \nu} p^{\mu} = 0$, and since $p^2 < 0$, we can choose a reference frame where $p^{\mu} = (p , 0 , ... , 0)$ only has a time component, leaving us with $S_{0 \nu} = 0$, implying that $\zeta _{0 \nu} = - \zeta _{\nu 0}$. This condition guarantees that the timelike components of $\zeta _{\mu \nu}$ have a positive contribution to its square $\zeta ^{\mu \nu} \zeta _{\mu \nu} = \zeta ^{i j} \zeta _{i j} + b , \ b = \zeta ^{0 i} \zeta _{0 i} > 0$, and the remaining part is spacelike thus must also have positive square, so we get that $\zeta ^{\mu \nu} \zeta _{\mu \nu} > 0$, so we are free of ghosts in the spin-2 spectrum.

It seems we're in trouble since eq \eqref{eqn:nth-spin-2-mass-shell} tells us we have no massless 2 excitation states, but in fact, this is not a problem and is actually expected since quantum geometric effects are expected to violate Lorentz invariance near the Planck scale \cite{Bodendorfer-LQG}, making it so massless particles effectively travel slightly slower than $c$, with corrections on the order of $\sim E_{pl} ^{- 4}$.

The fact that $G_{\mu \nu}$ is symmetric, traceless and satisfies $G_{\mu \nu} p^{\mu} = 0$ leaves it with
\begin{equation} \label{eqn:G-polarizations}
	\frac{1}{2} D (D - 1) - 1
\end{equation}
possible polarizations, which shows that indeed those polarizations fit nicely in a representation of $\mathrm{SO} (D - 1 , 1)$, \ie the traceless symmetric tensor representation, thus all our excited spin-2 states are consistent with Lorentz symmetry at the macroscopic scale even tho near the Planck scale they deviate a bit by having an effective mass.

@@

Following the general procedure given in \cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
\begin{equation}\label{eqn:polyakov-curved}
	S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
\begin{align}\label{eqn:polyakov-flat}
	S_{PB} = & -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} \nonumber     \\
	         & -\frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} + \nonumber \\
	         & + S_{int} [g , h , X].
\end{align}
